---
title: "R Notebook"
output: html_notebook
---


Load packages
```{r, message = FALSE, echo = FALSE, warning = FALSE}
library(janitor)
library(stringr)
library(reshape2)
library(Rcpp)
library(rstatix)
library(lme4)
library(lmerTest)
library(ggpubr)
library(grt)
library(tidyverse)
library(ggsci)
library(latex2exp)
options(digits=4)
```





# Load Data for REST contrasts (t = 4,16)

Load in and modify channel index
This file is used to label channel numbers
//TODO add left/right to chindex
```{r}
ch_index <- read.csv('channel_index.csv')

ch_index <- ch_index %>%
  mutate(NIRx_index = paste0(NIRx_src, '_', NIRx_det)) %>%
  mutate(fOLD_ch = paste0('ch_', fOLD_ch),
         NIRx_ch = paste0('ch_', NIRx_ch))

ch_index
```


Load the preprocessed HRF data.
This has been exported from the Homer3 environment.
```{r}

# setwd("C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/hrf/")
setwd("C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/nirs_group/beta_rest/")

nkey <- Sys.glob("*.csv")  #read in ppt filenames

rawbeta_restc <- list()  #Loads hrf into list while preserving key-value names
for (i in nkey){
  rawbeta_restc[[i]] <- read.csv(i, header = FALSE)
  print(i)
}

# rawbeta_restc[[4]]
# rawbeta_restc[[5]]
# rawbeta_restc[[6]]
# rawbeta_restc[[7]]

print(paste0("number of files: ", length(rawbeta_restc)))
```



Clean the beta data for rest condition
Get proper names, condition, orders etc.
```{r}
vch <- c()
for (i in 1:22){
  vch <- c(vch, paste0('ch_', i))
}
vch

lbeta <- list()   #make clean betas

for (i in names(rawbeta_restc)){
  
  print(i)
  
  lbeta[[i]] <- rawbeta_restc[[i]] %>%
    dplyr::select(V1, V2, V4) %>%
    rename('b_CATG' = 'V1',
           'b_CTRL' = 'V2',
           'b_REST' = 'V4') %>%
    mutate(NIRx_ch = vch) %>%            #assign nirx channel numbers
    mutate(pptid = substr(i, 1, 6)) %>%
    mutate(cond = substr(i, 8, 9)) %>%
    mutate(order = substr(i, 11, 11)) %>%
    left_join(ch_index, by = 'NIRx_ch') %>%
    dplyr::select(pptid, cond, order, fOLD_ch, b_CATG, b_CTRL, b_REST)
}

lbeta[[69]]  #show 1 listbeta


#Generate aggregate beta dataframe in long format
beta <- data.frame()
for(i in names(lbeta)){
  beta <- rbind(beta, lbeta[[i]])
}

#clean final beta dataframe

scalar = 1e4  #convert M to uM

beta_restc <- beta %>%
  mutate(b_CATG = b_CATG * scalar) %>%
  mutate(b_CTRL = b_CTRL * scalar) %>%
  mutate(b_REST = b_REST * scalar) %>%
  mutate(b_CATG = ifelse(b_CATG == 0, NA, b_CATG)) %>%
  mutate(b_CTRL = ifelse(b_CTRL == 0, NA, b_CTRL)) %>%
  mutate(b_REST = ifelse(b_REST == 0, NA, b_REST)) %>%
  mutate(catgrest = b_CATG - b_REST) %>%
  mutate(catgctrl = b_CATG - b_CTRL) %>%
  mutate(ctrlrest = b_CTRL - b_REST)

beta_restc
```




# Load Data for TASK contrasts (t = 5-20)

Load in and modify channel index
This file is used to label channel numbers
//TODO add left/right to chindex
```{r}
ch_index <- read.csv('channel_index.csv')

ch_index <- ch_index %>%
  mutate(NIRx_index = paste0(NIRx_src, '_', NIRx_det)) %>%
  mutate(fOLD_ch = paste0('ch_', fOLD_ch),
         NIRx_ch = paste0('ch_', NIRx_ch))

ch_index
```


Load the preprocessed HRF data.
This has been exported from the Homer3 environment.
```{r}

# setwd("C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/hrf/")
setwd("C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/nirs_group/beta_task/")

nkey <- Sys.glob("*.csv")  #read in ppt filenames

rawbeta_taskc <- list()  #Loads hrf into list while preserving key-value names
for (i in nkey){
  rawbeta_taskc[[i]] <- read.csv(i, header = FALSE)
  print(i)
}

# rawbeta_restc[[4]]
# rawbeta_restc[[5]]
# rawbeta_restc[[6]]
# rawbeta_restc[[7]]

print(paste0("number of files: ", length(rawbeta_taskc)))
```



Clean the beta data
Get proper names, condition, orders etc.
```{r}
vch <- c()
for (i in 1:22){
  vch <- c(vch, paste0('ch_', i))
}
vch

lbeta <- list()   #make clean betas
for (i in names(rawbeta_taskc)){
  lbeta[[i]] <- rawbeta_taskc[[i]] %>%
    dplyr::select(V1, V2, V4) %>%
    rename('b_CATG' = 'V1',
           'b_CTRL' = 'V2',
           'b_REST' = 'V4') %>%
    mutate(NIRx_ch = vch) %>%            #assign nirx channel numbers
    mutate(pptid = substr(i, 1, 6)) %>%
    mutate(cond = substr(i, 8, 9)) %>%
    mutate(order = substr(i, 11, 11)) %>%
    left_join(ch_index, by = 'NIRx_ch') %>%
    dplyr::select(pptid, cond, order, fOLD_ch, b_CATG, b_CTRL, b_REST)
}

lbeta[[69]]  #show 1 listbeta


#Generate aggregate beta dataframe in long format
beta <- data.frame()
for(i in names(lbeta)){
  beta <- rbind(beta, lbeta[[i]])
}

#clean final beta dataframe

scalar = 1e3 #convert M to uM

beta_taskc <- beta %>%
  mutate(b_CATG = b_CATG * scalar) %>%
  mutate(b_CTRL = b_CTRL * scalar) %>%
  mutate(b_REST = b_REST * scalar) %>%
  mutate(b_CATG = ifelse(b_CATG == 0, NA, b_CATG)) %>%
  mutate(b_CTRL = ifelse(b_CTRL == 0, NA, b_CTRL)) %>%
  mutate(b_REST = ifelse(b_REST == 0, NA, b_REST)) %>%
  mutate(catgrest = b_CATG - b_REST) %>%
  mutate(catgctrl = b_CATG - b_CTRL) %>%
  mutate(ctrlrest = b_CTRL - b_REST)

beta_taskc
```









# SECOND-LEVEL MODELING



## Behavioural Analyses

//TODO modeling and add into mixed models.

Define functions for extracting behavioural dataframe, flexible for both conditions.
```{r}
#wd must be this for behav_extract to work
setwd("C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/behav/")


#Takes two arguments, the participant number and the condition.
#returns cleaned behavioural data
behav_extract <- function(n, cond){
  
  
  #checks condition and extracts data based on condition
  if(cond == "CR"){
    behav_raw <- read.csv(paste0("behav_CR (", n ,").csv"))
  } else if (cond == "II"){
    behav_raw <- read.csv(paste0("behav_II (", n ,").csv"))
  } else {
    print("condition not specified")
    stop()
  }

  #clean data
  behav_tb <- behav_raw %>%
    as_tibble() %>%
    dplyr::select(participant, cpi, deg, keymap, stimID, keyLearn.keys, key_gaborTrial.keys) %>%
    mutate(stimID = na_if(stimID, ""),       #cleans "" and "None" entries
           keyLearn.keys = na_if(keyLearn.keys, ""),
           keyLearn.keys = na_if(keyLearn.keys, "None"),
           key_gaborTrial.keys = na_if(key_gaborTrial.keys, ""),
           key_gaborTrial.keys = na_if(key_gaborTrial.keys, "None"),
           keyLearn.keys = as.numeric(keyLearn.keys),
           key_gaborTrial.keys = as.numeric(key_gaborTrial.keys),
           keypress = coalesce(keyLearn.keys, key_gaborTrial.keys),
           corr = ifelse(is.na(keypress), NA, ifelse(keymap == keypress, 1, 0)), #checks if correct while maintaining null responses
           cond = cond) %>%
    drop_na(stimID) %>% #gets rid of trials that are not gabor
    dplyr::select(!c(keyLearn.keys, key_gaborTrial.keys))
  
  return(behav_tb)
}



#Takes tidy data from behav_extract() as input
#outputs performance curve df
behav_curve <- function(x){

  curve_tb <- x %>%
  mutate(block = c(rep(1, 60), rep(2, 60), rep(3, 60), rep(4, 60), rep(5, 60))) %>% #assign block number
  group_by(participant, cond, block) %>%
  mutate(corr = addNA(corr)) %>%
  count(corr, .drop = FALSE) %>%
  mutate(corr = as.character(corr)) %>%
  mutate(corr = ifelse(is.na(corr), "x", corr)) %>% #change na to 'x' for no response
  filter(corr == 1 | corr == 'x') %>%  #count num correct and na
  spread(corr, n) %>%
  rename(noresp = "x", corr = "1") %>%
  mutate(noresp = ifelse(is.na(noresp), 0, noresp)) %>%
  mutate(ntrial = 60 - noresp) %>%
  mutate(perf = corr / ntrial) %>%
  dplyr::select(participant, cond, block, perf)

  return(curve_tb)

}


#demo
setwd("C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/behav/")
x <- behav_extract(2, "CR")

  curve_tb <- x %>%
  mutate(block = c(rep(1, 60), rep(2, 60), rep(3, 60), rep(4, 60), rep(5, 60))) %>% #assign block number
  group_by(participant, cond, block) %>%
  mutate(corr = addNA(corr)) %>%
  count(corr, .drop = FALSE) %>%
  mutate(corr = as.character(corr)) %>%
  mutate(corr = ifelse(is.na(corr), "x", corr)) %>% #change na to 'x' for no response
  filter(corr == 1 | corr == 'x') %>%  #count num correct and na
  spread(corr, n) %>%
  rename(noresp = "x", corr = "1") %>%
  mutate(noresp = ifelse(is.na(noresp), 0, noresp)) %>%
  mutate(ntrial = 60 - noresp) %>%
  mutate(perf = corr / ntrial) %>%
  dplyr::select(participant, cond, block, perf)
  
curve_tb




# y <- behav_curve(x)
# 
# x
# y
```




Extract cleandata from all participants.
Extract separate files for CR/II and smush them together 
```{r}
#wd must be this for behav_extract to work
setwd("C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/behav/")

#extract CR data
pptperf_cr <- tibble()
for (i in 1:47){
  print(i)
  
  pptdat <- behav_extract(i, "CR")
  pptcurve <- behav_curve(pptdat)
  
  pptperf_cr <- rbind(pptperf_cr, pptcurve)
}

#extract II data
pptperf_ii <- tibble()
for (i in 1:45){
  print(i)
  
  pptdat <- behav_extract(i, "II")
  pptcurve <- behav_curve(pptdat)
  
  pptperf_ii <- rbind(pptperf_ii, pptcurve)
}

#combine
pptperf <- rbind(pptperf_cr, pptperf_ii)

pptperf_cr
pptperf_ii
pptperf

```


Brief viz together
```{r}
#get performance means and confidence intervals
vizdf <- pptperf %>%
  mutate(block = as.numeric(block)) %>%  #chg type for painfree plots
  group_by(cond, block) %>%  #yo group_by is a lit function you can group by more than just one variable
  summarise(perf_m = mean(perf, na.rm = TRUE),
            cilo = confint(lm(perf~1))[1],
            cihi = confint(lm(perf~1))[2])  #gets confidence interval on mean
#Note: the regression of an intercept only produces the mean perf~1

learncurve <- ggplot(data = vizdf,
       mapping = aes(x = block, y = perf_m)) + 
  geom_errorbar(aes(ymin = cilo, ymax = cihi, color = cond), size = 1, width = 0.1, position = position_dodge(width = 0.2)) +
  geom_point(aes(shape = cond, color = cond), size = 4, position = position_dodge(width = 0.2)) +
  geom_line(aes(linetype = cond, color = cond), size = 1) +
  scale_color_manual(name = "Condition", labels = c("RB", "II"), values = c("#086375", "#B9314F", "#5B3000", "#47682C", "#F9E0D9")) + 
  scale_shape_manual(name = "Condition", labels = c("RB", "II"), values = c(17,19)) +
  scale_linetype_manual(name = "Condition", labels = c("RB", "II"), values = c('solid', 'dashed')) +
  ylim(0.70, 0.95) +
  xlab("Blocks (60 trials)") +
  ylab("Accuracy") +
  theme_pubr() +
  theme(axis.line = element_line(colour = 'black', size = 1.5),
        axis.title.x = element_text(color="black", size= 16, face="bold", margin = margin(t = 10)),   #increase axis thickness
        axis.title.y = element_text(color="black", size= 16, face="bold", margin = margin(r = 10)),
        axis.text = element_text(color = "black", face = "bold", size = 14),
        legend.title = element_text(color = "black", face = "bold", size = 14),
        legend.text = element_text(color = "black", face = "bold", size = 10)) 

ggsave(plot = learncurve, "C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/outputs/exp3-learn-curve.png", dpi = 1000)
learncurve
```




Behavioural Stats

Repeated Measures ANOVA
```{r}
pptlist <- c('alnd06', 'amot96', 'anve09', 'asca01', 'asta05', 'aywa58', 'cang09', 'caon12', 'daer10', 'diry06', 'ebon04', 'elod06', 'elun02', 'enod03', 'erng43', 'eror06', 'errn04', 'erwa04', 'eyge08', 'ghon08', 'hare99', 'iaam10', 'iamm11', 'idod07', 'ieay11', 'inds03', 'irni08', 'ison04', 'juer07', 'lars98', 'lyor04', 'maan08', 'murn03', 'nand12', 'naod04', 'ngiu02', 'oele04', 'onia06', 'road04', 'saey06', 'sige01', 'yack04', 'yall02')

#Change variable types to run stats
aovdf <- pptperf %>%
  mutate(participant = factor(participant)) %>%
  mutate(block = factor(block)) %>%
  mutate(cond = factor(cond)) %>%
  ungroup() %>%
  filter(participant %in% pptlist)



aovdf

#Run ANOVA model
repaov <- anova_test(data = aovdf, 
                     dv = perf, 
                     wid = participant,
                     within = c(cond, block))

#Extract ANOVA parameters
get_anova_table(repaov)

```


Post-hoc main effect block for each condition
```{r}
ph_b <- pptperf %>%
  group_by(cond) %>%
  anova_test(dv = perf,
             wid = participant,
             within = block) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "holm")

ph_b

```

Pairwise block comparisons
```{r}
pwb <- pptperf %>%
  group_by(cond) %>%
  pairwise_t_test(
    formula = perf ~ block,
    paired = TRUE,
    p.adjust.method = "holm"
  )

pwb
```

pairwise condition comparisons
```{r}
ph_c <- pptperf %>%
  group_by(block) %>%
  anova_test(dv = perf,
             wid = participant,
             within = cond) %>%
  get_anova_table() %>%
  adjust_pvalue(method = "holm")

ph_c

```












## Strategy Modeling

//TODO modify function output for participant modeling instead of optimized for running simulations... (especially text output could probably be a dataframe or smg)

Function for fitting model and determining best fit with AIC Used below for error simulations
CR = Conjunctive, II = Info-Integ, FR = Freq Rule, OR = Orient Rule.
```{r}
#Function fits 4 categorization strategies and pulls AIC values for each
#pptdata: a dataframe input with columns - category, respones, cpi, deg
#plots: whether you want to see the decision bounds plotted, a boolean
modelfit <- function(pptdat, plots){
  
  #fits CR,II models
  cr_strat <- gcjc(keypress ~ cpi + deg, data = pptdat, category = pptdat$keymap, config = 1, zlimit=7)  #2D Conjunctive rule 
  ii_strat <- glc(keypress ~ cpi + deg, data = pptdat, category = pptdat$keymap, zlimit=7)     #2D information integration
  fr_strat <- glc(keypress ~ cpi, data = pptdat, category = pptdat$keymap, zlimit=7)           #1D frequency rule (fr)
  or_strat <- glc(keypress ~ deg, data = pptdat, category = pptdat$keymap, zlimit=7)           #1D orientation rule (or)

  #computes AIC for all models
  aic_report <- AIC(cr_strat, ii_strat, fr_strat, or_strat) #returns AIC 
  aic_report

  #gets AIC from aic_report, order of AIC values are hardcoded (CR, II, FR, OR)
  aicLabel <- c(aic_report$AIC)
  
  
  #prints plots 
  if (plots == TRUE){
    plot.gcjc(cr_strat)
    plot.glc(ii_strat)
  }

  return(aicLabel)
  
}
```



Extract raw response data
```{r}
#wd must be this for behav_extract to work
setwd("C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/behav/")

#extract CR data
pptresp_cr <- tibble()
for (i in 1:40){
  print(i)
  
  pptdat <- behav_extract(i, "CR") %>%
    na.omit %>%
    mutate(keymap = ifelse(keymap == 0, 2, 1)) %>% #changes 0->2 otherwise gcjc breaks
    mutate(keypress = ifelse(keypress == 0, 2, 1)) #changes 0->2 otherwise gcjc breaks
  
  pptresp_cr <- rbind(pptresp_cr, pptdat)
}

#extract II data
pptresp_ii <- tibble()
for (i in 1:38){
  print(i)
  
  pptdat <- behav_extract(i, "II") %>%
    na.omit() %>%
    mutate(keymap = ifelse(keymap == 0, 2, 1)) %>% #changes 0->2 otherwise gcjc breaks
    mutate(keypress = ifelse(keypress == 0, 2, 1)) #changes 0->2 otherwise gcjc breaks
    
  pptresp_ii <- rbind(pptresp_ii, pptdat) 
}

#combine
pptresp <- rbind(pptresp_cr, pptresp_ii) %>%
  mutate(ukey = paste0(participant, "_", cond))

pptresp
```





Fit the computational models and extract AIC
```{r}
pptid <- unique(pptresp$ukey)  #get unique pptid names

pptaic <- data.frame(matrix(ncol = 5, nrow = 1))
colnames(pptaic) <- c("ukey", "cr", "ii", "fr", "or")
pptaic

for (i in pptid){
  
  #dplyr::select only one unique key' (run) data
  moddf <- pptresp %>%
    filter(ukey == i)

  #run the model and acquire AICs
  tempaic <- modelfit(moddf, plots = FALSE)
  tempaic <- c(i, tempaic) #add pptid

  pptaic <- rbind(pptaic, tempaic)
  
}

pptaic <- pptaic %>%
  na.omit() %>%
  mutate(strat = ifelse(ii < cr & ii < fr & ii < or,   #checks if ii is bestfit, otherwise it is rb
                        'ii',
                        'rb')) %>%
  mutate(strat = factor(strat, levels = c("rb", "ii"))) %>%
  mutate(bound = ifelse(ii < cr & ii < fr & ii < or,
                        'ii',
                        ifelse(cr < ii & cr < fr & cr < or,
                               'cr',
                               'rb'))) %>%
  mutate(bound = factor(bound, levels = c("ii", "rb", "cr")))

pptaic
```





//TODO visualize proportions in barchart
```{r}
prop_df <- pptaic %>%
  mutate(cond = substr(ukey, 8,9)) %>%
  group_by(cond, strat) %>%
  summarise(count = n(),
            prop = count / (nrow(pptaic) / 2),
            se = sqrt((prop * (1-prop)) / sum(count))) %>%
  mutate(sehi = prop + se) %>%
  mutate(selo = prop - se) %>%
  mutate(selo = ifelse(selo < 0, 0.01, selo))

prop_df


stratprop <- ggplot(prop_df, aes(fill = strat, x = cond, y = prop)) +
  geom_bar(aes(fill = strat), color = "black", position = "dodge", stat = "identity", width = .5) +
  geom_errorbar(aes(ymin = selo, ymax = sehi, color = strat), color = "black", size = 1, width = 0.1, position = position_dodge(width = 0.5)) +
  scale_fill_manual(name = "Model Strategy", labels = c("RB", "II"), values = c("#086375", "#B9314F", "#5B3000", "#47682C", "#F9E0D9")) + 
  scale_x_discrete(labels = c("RB", "II")) +
  ylim(0,1) +
  xlab("Experimental Condition") +
  ylab("Proportion of Best Fit Model") +
  theme_pubr() +
  theme(axis.line = element_line(colour = 'black', size = 1.5),
        axis.title.x = element_text(color="black", size= 16, face="bold", margin = margin(t = 10)),   #increase axis thickness
        axis.title.y = element_text(color="black", size= 16, face="bold", margin = margin(r = 10)),
        axis.text = element_text(color = "black", face = "bold", size = 14),
        legend.title = element_text(color = "black", face = "bold", size = 14),
        legend.text = element_text(color = "black", face = "bold", size = 10)) 

# ggsave("C:/Users/Tim/Google Drive/category/analysis/outputs/strat-prop.png", dpi = 600)

stratprop

ggsave(plot = stratprop,
       filename = "C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/outputs/exp3-strat-prop.png",
       width = 7,
       height = 7,
       units = "in",
       dpi = 1000)
```







## Mixed Modeling

//TODO add computational modelings
//TODO add all relevant contrasts into the same dataframe...


```{r}
#Clean the behavioural dataframe
df_perf = pptperf %>%
  filter(block == 3 | block == 4 | block == 5) %>%
  group_by(participant, cond) %>%
  summarise(m_perf = mean(perf, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(z_perf = (m_perf - mean(m_perf)) / sd(m_perf))

df_perf
```



gather results in a clean dataframe
double left join to both the behavioural and modeling data
```{r}
vch <- c()
for (i in 1:18){
  vch <- c(vch, paste0('ch_', i))
}

dfmixmod <- beta_restc %>%
  dplyr::select(!c(b_CATG, b_CTRL, b_REST, ctrlrest)) %>%
  left_join(df_perf, by = c('pptid' = 'participant', 'cond' = 'cond')) %>%
  mutate(ukey = paste0(pptid, '_', cond)) %>%
  relocate(ukey) %>%
  left_join(pptaic, by = 'ukey') %>%
  dplyr::select(fOLD_ch, pptid, cond, order, strat, bound, z_perf, catgrest, catgctrl) %>%
  rename(zperf = z_perf) %>%
  mutate(pptid = factor(pptid),
         cond = factor(cond, levels = c('II', 'CR')),
         order = factor(order),
         strat = factor(strat, levels = c('ii', 'rb')))

dfmixmod

```






Run the model channel-wise and refine to acquire significant predictors  FULL MODEL
```{r, echo = T, results = 'hide'}
modlist <- list()
reflist <- list()
for (i in vch){
  
  #channel wise modeling
  dfchmod <- dfmixmod %>%
    filter(fOLD_ch == i) %>%
    na.omit()
  
  lmod <- lm(formula = catgrest ~ order * zperf * cond, data = dfchmod)

  refmod <- step(lmod, direction = 'both')
  
  modlist[[i]] <- summary(lmod)
  reflist[[i]] <- summary(refmod)
}
```





Show full model results
```{r}
for (i in names(modlist)){
   print(i)
   print(modlist[[i]])
}
```


Show refined model results
```{r}
#print model results
for (i in names(reflist)){
   print(i)
   print(reflist[[i]])
}
```




Gather and show only models with significant fixed effects
```{r}
siglist <- list()

for (i in names(reflist)){
  
  checkdf <- reflist[[i]]$coefficients %>%  #grab fixed effects dataframe from refined model
    as.data.frame() %>%
    rename("pval" = "Pr(>|t|)")
  
  checkp <- checkdf$pval   #grab vector of pvalues on F of regressor
  
  if (any(checkp < .05)){   #if any significant regressors
    siglist[[i]] <- reflist[[i]]  #store model object with 
    print(i)
    print(reflist[[i]])  #print to show significant 
    print("-----------------------------------------------------------------")
  }
  
}
```





Gather results of full models in one dataframe (statdf)
```{r}
fullstatdf <- data.frame() #initialize

for (i in names(modlist)){
  
  tempstat <- coef(modlist[[i]]) %>%
    data.frame() %>%
    rename(beta = Estimate,
          se = Std..Error,
          t = t.value,
          p = Pr...t..) %>%
    rownames_to_column(var = "reg") %>%
    mutate(reg = ifelse(reg == "(Intercept)", "int", reg)) %>% #change "intercept" to "int"
    dplyr::select(reg, beta, se, t, p) %>%
    mutate(ch = i) %>%
    relocate(ch)
  
  fullstatdf <- rbind(fullstatdf, tempstat)
  
}

fullstatdf <- fullstatdf %>%
  filter(ch != 'ch_19' & ch != 'ch_20', ch != 'ch_21', ch != 'ch_22') %>%
  mutate(mod = "full") %>%
  relocate(mod, .after = ch) %>%
  mutate(testid = paste0(ch, "_", reg)) %>%
  relocate(testid)

fullstatdf
```




Gather results of refined, significant models into one dataframe
```{r}
sigstatdf <- data.frame() #initialize

for (i in names(siglist)){
  
  print(i)
  
  tempstat <- siglist[[i]] %>%
    coef() %>%
    data.frame() %>%
    rename(beta = Estimate,
          se = Std..Error,
          t = t.value,
          p = Pr...t..) %>%
    rownames_to_column(var = "reg") %>%
    mutate(reg = ifelse(reg == "(Intercept)", "int", reg)) %>% #change "intercept" to "int"
    dplyr::select(reg, beta, se, t, p) %>%
    mutate(ch = i) %>%
    relocate(ch)
    

  sigstatdf <- rbind(sigstatdf, tempstat)

}

sigstatdf <- sigstatdf %>%
  filter(ch != 'ch_19' & ch != 'ch_20', ch != 'ch_21', ch != 'ch_22') %>%
  mutate(mod = "sig") %>%
  relocate(mod, .after = ch) %>%
  mutate(testid = paste0(ch, "_", reg)) %>%
  relocate(testid)

sigstatdf
```



Combine significant models with insignificant model results
```{r}

aggstatdf <- fullstatdf %>%
  filter(!(testid %in% sigstatdf$testid)) %>%
  rbind(sigstatdf) %>%
  mutate(ch_n = substring(ch, 4)) %>%
  mutate(ch_n = as.numeric(ch_n)) %>%
  relocate(ch_n, .after = ch) %>%
  arrange(ch_n)

aggstatdf

```








Print to file the stats associated with condition
```{r}
sigcond <- aggstatdf %>%
  # filter(p < .05) %>%
  # filter(grepl(pattern = "condCR", x = reg, ignore.case = TRUE)) %>%
  filter(reg == "condCR") %>%
  rename(fOLD_ch = ch, statistic = t) %>%
  left_join(ch_index) %>%
  rename(channel = fOLD_ch,
         tstat = statistic,
         sens = Sensitivity) %>%
  dplyr::select(channel, reg, beta, se, tstat, p, sens, ROI_BA, x, y, z, Side)
  # mutate(padj = p.adjust(p, method = "fdr", n = 6)) %>%
  # relocate(padj, .after = p)
  

sigcond
write.csv(sigcond, "C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/visdf/mod_crii_cond.csv")

```





Print to file the stats associated with perf
```{r}
sigperf <- aggstatdf %>%
  # filter(p < .05) %>%
  # filter(grepl(pattern = "zperf", x = reg, ignore.case = TRUE)) %>%
  filter(reg == "zperf") %>%
  rename(fOLD_ch = ch, statistic = t) %>%
  left_join(ch_index) %>%
  rename(channel = fOLD_ch,
         tstat = statistic,
         sens = Sensitivity) %>%
  select(channel, reg, beta, se, tstat, p, sens, ROI_BA, x, y, z, Side)

sigperf
write.csv(sigperf, "C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/visdf/mod_crii_zperf.csv")

```




Print to file the stats associated with perf:condCR
```{r}
sigperf <- aggstatdf %>%
  # filter(p < .05) %>%
  filter(reg == "zperf:condCR") %>%
  rename(fOLD_ch = ch, statistic = t) %>%
  left_join(ch_index) %>%
  rename(channel = fOLD_ch,
         tstat = statistic,
         sens = Sensitivity) %>%
  select(channel, reg, beta, se, tstat, p, sens, ROI_BA, x, y, z, Side) %>%
  arrange(desc(tstat))

sigperf
write.csv(sigperf, "C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/visdf/mod_crii_zperfcondCR.csv")

```











Visualizing effect of performance interaction with condition on activation

```{r}
plotdf <- dfmixmod %>%
  filter(fOLD_ch == "ch_16")

ch16_condperfint <- ggplot(data = plotdf,
       mapping = aes(x = zperf,
                     y = catgrest,
                     color = cond,
                     shape = cond)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", fullrange = TRUE, size = 2, se = FALSE) +
  scale_color_manual(name = "Condition", labels = c("II", "RB"), values = c("#B9314F", "#086375",  "#5B3000", "#47682C", "#F9E0D9")) + 
  scale_shape_manual(name = "Condition", labels = c("II", "RB"), values = c(17,19)) +
  ylim(-20,20) +
  xlim(-3, 3) +
  xlab("Performance (z-scored)") +
  ylab(TeX("$\\beta_{CATG} > \\beta_{REST}$")) +
  theme_pubr() +
  theme(axis.line = element_line(colour = 'black', size = 1.5),
        axis.title.x = element_text(color="black", size= 16, face="bold", margin = margin(t = 10)),   #increase axis thickness
        axis.title.y = element_text(color="black", size= 16, face="bold", margin = margin(r = 10)),
        axis.text = element_text(color = "black", face = "bold", size = 14),
        legend.title = element_text(color = "black", face = "bold", size = 14),
        legend.text = element_text(color = "black", face = "bold", size = 10),
        aspect.ratio = 1,
        legend.position = "none") 


ch16_condperfint

ggsave(plot = ch16_condperfint, "C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/outputs/exp3-ch16-condperfint.png",
       height = 7,
       width = 7,
       dpi = 1000)

```


```{r}
plotdf <- dfmixmod %>%
  filter(fOLD_ch == "ch_6")

ch6_condperfint <- ggplot(data = plotdf,
       mapping = aes(x = zperf,
                     y = catgrest,
                     color = cond,
                     shape = cond)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", fullrange = TRUE, se = FALSE, size = 2) +
  scale_color_manual(name = "Condition", labels = c("II", "CR"), values = c("#B9314F", "#086375",  "#5B3000", "#47682C", "#F9E0D9")) +
  scale_shape_manual(name = "Condition", labels = c("II", "CR"), values = c(17,19)) +
  ylim(-20,20) +
  xlim(-2, 2) +
  xlab("Performance (z-scored)") +
  ylab(TeX("$\\beta_{CATG} > \\beta_{REST}$")) +
  theme_pubr() +
  theme(axis.line = element_line(colour = 'black', size = 1.5),
        axis.title.x = element_text(color="black", size= 16, face="bold", margin = margin(t = 10)),   #increase axis thickness
        axis.title.y = element_text(color="black", size= 16, face="bold", margin = margin(r = 10)),
        axis.text = element_text(color = "black", face = "bold", size = 14),
        legend.title = element_text(color = "black", face = "bold", size = 14),
        legend.text = element_text(color = "black", face = "bold", size = 10),
        aspect.ratio = 1,
        legend.position = "none") 


ch6_condperfint

ggsave(plot = ch6_condperfint, "C:/Users/user00/My Drive/category_fNIRS/exp3_analysis/outputs/exp3-ch6-condperfint.png",
       height = 7,
       width = 7,
       dpi = 1000)
```









# DIAGNOSTICS


```{r}

dfchmod <- dfmixmod %>%
  filter(fOLD_ch == "ch_16")
lmod <- lm(formula = catgrest ~ order * zperf * cond, data = dfchmod)
rmod <- step(lmod)

summary(rmod)

plot(rmod)
```


```{r}
tempstat <- coef(modlist[[i]]) %>%
    data.frame() %>%
    rename(beta = Estimate,
          se = Std..Error,
          t = t.value,
          p = Pr...t..) %>%
    rownames_to_column(var = "reg") %>%
    mutate(reg = ifelse(reg == "(Intercept)", "int", reg)) %>% #change "intercept" to "int"
    select(reg, beta, se, t, p) %>%
    mutate(ch = i) %>%
    relocate(ch)

tempstat
```








Run the model channel-wise and refine to acquire significant predictors
```{r}
modlist <- list()
reflist <- list()
for (i in vch){
  
  #channel wise modeling
  dfchmod <- dfmixmod %>%
    filter(fOLD_ch == i) %>%
    na.omit()
  
  lmod <- lmer(formula = catgrest ~ (1 | order) + (1 | pptid) + zperf * cond, data = dfchmod, REML = FALSE)

  refmod <- step(lmod, direction = 'both')
  
  modlist[[i]] <- summary(lmod)
  reflist[[i]] <- refmod
}
```


Show full model results
```{r}
for (i in names(modlist)){
   print(i)
   print(modlist[[i]])
}
```


Show refined model results
```{r}
#print model results
for (i in names(reflist)){
   print(i)
   print(reflist[[i]])
}
```




Gather and show only models with significant fixed effects
```{r}
siglist <- list()

for (i in names(reflist)){
  
  checkdf <- reflist[[i]]$fixed %>%  #grab fixed effects dataframe from refined model
    as.data.frame() %>%
    rename("pval" = "Pr(>F)")
  
  checkp <- checkdf$pval   #grab vector of pvalues on F of regressor
  
  if (any(checkp < .05)){   #if any significant regressors
    siglist[[i]] <- reflist[[i]]  #store model object with 
    print(i)
    print(reflist[[i]])  #print to show significant 
    print("-----------------------------------------------------------------")
  }
  
}
```







